%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.

% NOAH'S TODOS
% Add BOLDED keywords into descriptions
% go over his with doug/others
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{yoshi}
\usepackage{fontawesome}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Noah}{Yoshida}{ \urlstyle{same}\url{github.com/noyoshi} \\
\href{nyoshida@nd.edu}{\faEnvelope \ nyoshida@nd.edu} | \faMobile\ 785.766.8047
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of Notre Dame}
\descript{B.S. Computer Engieering}
\location{Expected May 2020 | Notre Dame, IN}
Dean's List (All Semesters) \\
\location{ Cum. GPA: 3.819 / 4.0 \\
Major GPA: 4.0 / 4.0}
\sectionsep

\subsection{University of Kansas}
\descript{Non-Degree Seeking Student}
\location{Jan 2015 - May 2015 | Lawrence, KS}
\location{ Cum. GPA: 4.0 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
\faGithub \ GitHub:// \href{https://github.com/noyoshi}{\custombold{noyoshi}} \\
\faLinkedin \ LinkedIn://  \href{https://www.linkedin.com/in/noah-yoshida-bba9b0136}{\custombold{noah-yoshida-bba9b0136}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\descript{Fall 2017}
Fundamentals of Computing \\
Discrete Math\\
Programming Challenges \\
{\footnotesize \textit{\textbf{\custombold{(Junior-Level Course)} }}} \\
\sectionsep
\descript{Spring 2018}
Data Structures and Algorithms \\
Logic Design \\
Systems Programming \\
Database Fundamentals \\
{\footnotesize \textit{\textbf{\custombold{(Junior-Level Course)} }}} \\
Research Assistant - Professor Chiang \\
{\footnotesize \textit{\textbf{\custombold{(Machine Learning, NLP)} }}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\descript{Proficient}
Python \textbullet{} C++ \textbullet{} MATLAB \\
\descript{Familiar}
JavaScript \textbullet{} SQL \\
\sectionsep
\subsection{Formatting}
\descript{Proficient}
HTML \textbullet{} CSS \textbullet{} Markdown \\
\LaTeX\ \\
\sectionsep
\subsection{Other}
Linux \textbullet{} TensorFlow \textbullet{} Django \\
Web-Scrapping \textbullet{} Neural Networks \\
UX/UI Design \textbullet{} Git \\
Full Stack Web Development \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.65\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS SINCE I HAVE NO WORK EXP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{OtakuMe}
\descript{| Creator }
\location{Oct 2017 - Current | Notre Dame, IN}
\location{\faGithub \ \href{https://github.com/noyoshi/OtakuMe}{github.com/noyoshi/OtakuMe}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Full stack web application, which allows users to make meaningful searches for favorite anime / manga series, and discover new series based on their search.
\item Created back end using Python + Django and SQLite, and front end UI with the bootstrap framework along with custom CSS and Javascript.
\end{tightemize}
\sectionsep

\runsubsection{Chkr.io}
\descript{| Team Member }
\location{Oct 2017 | Columbia, MO}
\location{\faGithub \ \href{https://github.com/noyoshi/TigerHacks}{github.com/noyoshi/TigerHacks}}
\begin{tightemize}
\item Full stack web application which provides users with fact accuracy and information consensus relating to news articles and reddit threads. \item Created the front-end UI with Materialze CSS + Javascript, and the back-end web scrapers with Python. \item Project was created and demo'ed at TigerHacks, a hackathon sponored by the University of Missourri. \end{tightemize}
\sectionsep

\runsubsection{Japanese + English Neural Network}
\descript{| Team Member}
\location{April 2017 – May 2017 | Notre Dame, IN}
\location{\faGithub \ \href{https://github.com/noyoshi/language-nn-matlab}{github.com/noyoshi/language-nn-matlab}}
\begin{tightemize}
\item Neural network written in MATLAB for my Intro to Engineering final project. It determined the language of a word users put in, with over 90\% accuracy.  \item Wrote the functions for input processing, back propagation, and training. \item Created both single layer and multi layer networks to test how additional layers affect performance. \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work}
\runsubsection{Oracle Japan}
\descript{| Management Consulting Intern}
\location{Jun 2017 – Jul 2017 | Tokyo, JP}
Worked with other interns to analyze Oracle Japan's IaaS + PaaS business strategy.
Interviewed senior executives and employees to determine operational risks, and presented findings to senior management as a group, along with possible solutions.
\sectionsep

\runsubsection{Office of Undergraduate Admissions} \\
\descript{Reilly Student Committee Member}
\location{Mar 2017 – Present | Notre Dame, IN}
Works with the Office of Undergraduate Admissions and fellow committee members to plan and run the Reilly Program, a recruiting program that brings top applicants to the University of Notre Dame.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Honors + Awards}
\begin{tabular}{rll}
2016	     & Merit Scholarship  & Notre Dame Scholar's Program\\
2016	     & Honors Program  & Glynn Family Honor's Program\\
2016	     & Honors Program  & Building Bridges Mentoring Program\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Extra curriculars
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Clubs + Activities}

\begin{tabular}{rll}
2016   & Merit Program    & Notre Dame Merit Scholars\\
2016   &  University  & Linux User's Group (LUG)\\
2016   &  University   & Asian American Association\\
\end{tabular}
\sectionsep

\end{minipage}
\end{document}
